---
docname: Curriculum Vitae
name: Fan Cheng
address: "Department of Econometrics & Business Statistics,\\tabularnewline Monash University, VIC 3800, Australia."
www: fancheng.me
# phone: +61 3 9905 1385
email: "Fan.Cheng@monash.edu"
twitter: fanchengfc
github: ffancheng
linkedin: fan-cheng
orcid: 0000-0003-0009-3262
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "880020"
output: 
  vitae::hyndman: 
    keep_tex: true
header_includes:
  - \ExecuteBibliographyOptions{useprefix=true}
  - renewcommand{\bibfont}{\normalfont\fontsize{12}{15}\sffamily}
  - \usepackage{hanging}
  - \parindent=1pt
  - \parskip=\medskipamount
  # - \pagenumbering{gobble}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)
source("baretable.R")
```

\thispagestyle{empty}

# Education and qualifications

\begin{tabular}{lll}
  2019-- & Ph.D. in Statistics & Monash University, Australia \\ 
        & Thesis: & \emph{Manifold Learning on Empirical Probability Distributions} \\
        & Supervisors: & \href{https://robjhyndman.com/}{Prof. Rob J Hydman} and \href{https://anastasiospanagiotelis.netlify.app/}{A/Prof. Anastasios Panagiotelis} \\        
  2016--2018 & M. in Applied Statistics & Central University of Finance and Economics, China \\ 
        & Supervisor: & \href{https://feng.li/}{A/Prof. Feng Li} \\
  2012--2016 & B.Ec in Statistics & Central University of Finance and Economics, China \\ 
\end{tabular}
  
```{r degrees, results='asis', eval=FALSE}
tribble(
  ~Start, ~End, ~Degree, ~Institution,
  2019, NA, "Ph.D. in Statistics", "Monash University, Australia",
  # NA, NA, "Supervisors: \\href{https://robjhyndman.com/}{Prof. Rob J Hydman} and \\href{https://anastasiospanagiotelis.netlify.app/}{A/Prof. Anastasios Panagiotelis}", NA, 
  2016, 2018, "M. in Applied Statistics", "Central University of Finance and Economics, China",
  2012, 2016, "B.Ec in Statistics", "Central University of Finance and Economics, China"
) %>%
  # arrange(-Start) %>%
  mutate(End = replace_na(as.character(End), "")) %>%
  mutate(Years = paste(Start, "--", End, sep = "")) %>%
  select(Years, Degree, Institution) %>%
  baretable()
```

# Working papers

\hangindent=0.5em\hangafter=0
Cheng, F., Hyndman, R. J., & Panagiotelis, A. (2021). Computationally Efficient Learning of Statistical Manifolds. arXiv 

\hangindent=2em\hangafter=0 preprint arXiv:2103.11773. (Under review)

\hangindent=0.5em\hangafter=0
Cheng, F., Panagiotelis, A., & Hyndman, R. J. (2022). Distortion-corrected kernel density estimate on Riemannian

\hangindent=2em\hangafter=0 manifolds.

# Research experience

<!-- # ```{r researchmlann, results='asis'} -->
<!-- # awards <- tribble( -->
<!-- #   ~Start, ~End, ~Project, -->
<!-- #   2019.02, NA, "\\textbf{Main Participant}, Monash Ph.D. project: Manifold Learning on Empirical Probability Distributions", -->
<!-- # ) %>% -->
<!-- #   arrange(-Start) %>% -->
<!-- #   mutate(End = replace_na(as.character(End), "")) %>% -->
<!-- #   mutate(Years = paste(Start, "--", End, sep = "")) %>% -->
<!-- #   select(Years, Project) %>% -->
<!-- #   baretable() -->
<!-- # ``` -->
<!-- # -->
<!-- #   * Supervised by [Prof. Rob J Hyndman](https://robjhyndman.com) and [Associate Prof. Anastasios Panagiotelis](https://anastasiospanagiotelis.netlify.app/). -->
<!-- #   * Successfully completed the confirmation and the mid-candidature milestones. -->
<!-- #   * Completed the main algorithm and finished all experiments using MonARCH HPC Cluster. -->
<!-- #   * Submitted the working paper titled [*Computationally Efficient Learning of Statistical Manifolds*](https://arxiv.org/abs/2103.11773). -->

```{r researchcufe, results='asis'}
awards <- tribble(
  ~Start, ~End, ~Project,
  2018.07, 2019.01, "\\textbf{Research Assistant}, National Natural Science Foundation of China Project",
) %>%
  arrange(-Start) %>%
  mutate(End = replace_na(as.character(End), "")) %>%
  mutate(Years = paste(Start, "--", End, sep = "")) %>%
  select(Years, Project) %>%
  baretable()
```
  
  * Assisted in the project *Efficient Bayesian Flexible Density Methods with High Dimensional Financial Data*.
  * Completed the stochastic gradient descent application of housing price to the multivariate response surface model.
  * Completed the thesis titled *Volatility Analysis of Housing Prices with Bayesian Response Surface Optimization*.

```{r researchietp, results='asis'}
awards <- tribble(
  ~Start, ~End, ~Project,
  2013.04, 2014.04, "\\textbf{Main Participant}, National Undergraduate Innovation and Entrepreneurship Training Program of China",
) %>%
  arrange(-Start) %>%
  mutate(End = replace_na(as.character(End), "")) %>%
  mutate(Years = paste(Start, "--", End, sep = "")) %>%
  select(Years, Project) %>%
  baretable()
```
  
  * Initiated a municipal project, made overall arrangements for the project, from research proposal, project fund application, plan of the theoretical approaches and empirical analysis of the questionnaire data.
  * Won the Excellent Prize upon the accomplishment of the research project.
  * Completed the paper titled *Feasibility Analysis for Developing Commercial Insurance for Losing Only-child Problem*.


# Teaching experience

```{r employment, results='asis'}
tribble(
  ~Start, ~End, ~Position,
  2020.07, NA, "\\textbf{Teaching Associate}, Department of Econometrics and Business Statistics, Monash University",
  NA, NA, "- \\href{https://handbook.monash.edu/2021/units/ETC5513?year=2021}{ETC5513 Collaborative and reproducible practices, 2021S1, 2022S2}",
  NA, NA, "- \\href{https://handbook.monash.edu/2021/units/ETC5523?year=2021}{ETC5523 Communicating with data, 2021S2}",
  NA, NA, "- \\href{https://handbook.monash.edu/2020/units/ETF5500?year=2020}{ETF3500/ETF5500 High Dimensional Data Analysis, 2020S2, 2021S2}",
  2019.07, NA, "\\textbf{Data Fluency Associate Instructor}, Library Research Division, Monash University Library",
   NA, NA, "- \\href{https://www.monash.edu/data-fluency/home}{Monash Data Fluency introductory and intermidiate workshops} on R, Python, Git, Unix, HPC, etc.",
  2020.07, 2020.12, "\\textbf{Course Mentor}, Monash University Online Microcredential \\href{https://www.futurelearn.com/microcredentials/data-driven-decision-making?utm_source=faculty_website&utm_medium=monash_organic_referrer&utm_campaign=mc_jan}{\\textit{Data Science: Data-Driven Decision Making}}"
) %>%
  # arrange(-Start) %>%
  mutate(End = replace_na(as.character(End), "")) %>%
  mutate(Years = paste(Start, "--", End, sep = "")) %>%
  mutate(Years = ifelse(is.na(Start), "", Years)) %>% 
  select(Years, Position) %>%
  baretable()
```

# Conference presentations

<!-- \hangindent=0.5em\hangafter=0 -->

<!-- - Invited talk, Anomaly detection and forecasting using machine learning methods, \href{http://www.cfenetwork.org/CFE2022/index.php}{The 16th International Conference on Computational and Financial Econometrics (CFE 2022)}, King's College London, UK, December 17-19, 2022. -->

- Contributed talk, Anomaly detection with kernel density estimation on manifolds, \href{http://www.compstat2022.org/index.php}{The 24th International Conference on Computational Statistics}, The University of Bologna, Italy, August 23-26, 2022.

- Contributed talk, Manifold learning with approximate nearest neighbors, \href{http://ecssc2021.com.au/}{Early Career and Student Statisticians Conference 2021}, online, July 30, 2021.

- Participants talk, Manifold learning with approximate nearest neighbors, \href{https://ws.amsi.org.au/}{Australian Mathematical Sciences Institute (AMSI) Winter School 2021}, online, July 16, 2021.

- Short interactive talk, Computationally efficient learning of statistical manifolds, \href{https://iasc-isi.org/dssv-ecda2021/}{Data Science, Statistics and Visualisation (DSSV) and European Conference on Data Analysis (ECDA)}, online, July 8, 2021.

- Contributed talk, Manifold learning with approximate nearest neighbors, \href{https://anzsc2021.com.au/}{Australian Statistical Society and New Zealand Statistical Association Conference 2021}, Melbourne (Hybrid), July 6, 2021.

- Contributed talk, Getting it right: improving forecast accuracy and learning techniques Session, Monash Business School Doctoral Research Colloquium, Melbourne, December 6, 2020.

<!-- ```{r conference, results='asis'} -->
<!-- tribble( -->
<!--   ~Time, ~Title, ~Conference, ~Location, -->
<!--   "2021.07.30", "Manifold learning with approximate nearest neighbors", "\\href{http://ecssc2021.com.au/}{Early Career and Student Statisticians Conference 2021}", "Australia (Online)", -->
<!--   "2021.07.16", "Manifold learning with approximate nearest neighbors", "\\href{https://ws.amsi.org.au/}{Australian Mathematical Sciences Institute (AMSI) Winter School 2021}", "Hybrid Event Hosted By Queensland University of Technology", -->
<!--   "2021.07.06", "Manifold learning with approximate nearest neighbors", "\\href{https://anzsc2021.com.au/}{Australian Statistical Society and New Zealand Statistical Association Conference 2021}", "Australia (Hybrid)" -->
<!-- ) %>% -->
<!--   # arrange(-Start) %>% -->
<!--   # mutate(End = replace_na(as.character(End), "")) %>% -->
<!--   # mutate(Years = paste(Start, "--", End, sep = "")) %>% -->
<!--   # select(Years, Position) %>% -->
<!--   baretable() -->
<!-- ``` -->

# Internship experience

```{r internship, results='asis'}
tribble(
  ~Start, ~End, ~Position,
  2016.09, 2017.09, "\\textbf{Big Data Analyst}, Shanghai Power Xene Digital Technology Company, Beijing, China",
  2016.03, 2016.04, "\\textbf{Research Assistant}, China Life Insurance Company Limited, Beijing, China",
  2015.01, 2015.02, "\\textbf{Consultant Assistant}, Industrial and Commercial Bank of China (ICBC), Hubei, China",
) %>%
  arrange(-Start) %>%
  mutate(End = replace_na(as.character(End), "")) %>%
  mutate(Years = paste(Start, "--", End, sep = "")) %>%
  select(Years, Position) %>%
  baretable()
```

# Society memberships

```{r society, results='asis'}
tribble(
  ~Position, ~Society,
  "Member", "Statistical Society of Australia (SSA)",
  "Member", "International Association for Statistical Computing (IASC)",
  "Member", "Australian Research Council Centre of Excellence for Mathematical and Statistical Frontiers (ACEMS)"
) %>%
  # arrange(-Start) %>%
  # mutate(End = replace_na(as.character(End), "")) %>%
  # mutate(Years = paste(Start, "--", End, sep = "")) %>%
  # select(Years, Position) %>%
  baretable()
```

# Computer skills

```{r computer, results='asis'}
tribble(
  ~language,
  "Proficient in R, Git/GitHub, LaTex",
  "Skilled in GNU/Linux and have experience on high performance Linux clusters",
  "Intermediate in Python, HTML/CSS"
) %>%
  # arrange(-Start) %>%
  # mutate(End = replace_na(as.character(End), "")) %>%
  # mutate(Years = paste(Start, "--", End, sep = "")) %>%
  # select(Years, Position) %>%
  baretable()
```

# Honours and awards

\begin{tabular}{rl}
  2022 & Graduate Research Completion Award (GRCA), Monash University \\
  2022 & Purple Letter (Outstanding Unit Evaluation of Teaching) for Tutoring ETC5513 2022S1, Monash Business School \\ 
  2022 & Purple Letter for Tutoring ETF3500 2021S2, Monash Business School \\ 
  2021 & Purple Letter for Tutoring ETC5513 2021S1, Monash Business School \\ 
  2021 & Runner-up for AMSI Winter School Participants Talk, \href{https://ws.amsi.org.au/}{Australian Mathematical Sciences Institute} \\ 
  2021 & ACEMS Business Analytics Prize(\$3000) for 2021, \href{https://acems.org.au}{ARC Centre of Excellence for Mathematical \& Statistical Frontiers} \\ 
  2019 & Monash Graduate Scholarship, Monash University, yearly from 2019 to 2022 \\ 
  2019 & Monash International Tuition Scholarship, Monash University, yearly from 2019 to 2022 \\ 
  2018 & Outstanding Postgraduate Student, Central University of Finance and Economics (CUFE) \\ 
  2017 & First Prize Academic Scholarship for Graduate Student, CUFE \\ 
  2016 & Outstanding Undergraduate Student, CUFE \\ 
  2016 & Scholarship for All-Round Development, CUFE, yearly from 2013 to 2016 \\ 
  2016 & Scholarship for Excellent Academic Innovation, CUFE \\ 
  2015 & Excellent Prize in National Undergraduate Statistical Contest in Modeling, Statistical Education Society of China \\ 
  2015 & Second Prize in Contemporary Undergraduate Mathematical Contest in Modeling, China Society for Industrial \\
       & and Applied Mathematics \\ 
  2015 & National Endeavor Scholarship, Beijing Municipal Commission of Education \\ 
  2014 & Scholarship for Excellent Student Cadre, CUFE \\ 
  2013 & Excellent Student Cadre, School of Statistics and Mathematics, CUFE \\ 
\end{tabular}
  
```{r awards, results='asis', eval=FALSE}
awards <- tribble(
  ~Year, ~Award,
  2022, "Purple Letter (Outstanding Unit Evaluation of Teaching) for Tutoring ETC5513 2022S1, Monash Business School",
  2022, "Purple Letter for Tutoring ETF3500 2021S2, Monash Business School", 
  2021, "Purple Letter for Tutoring ETC5513 2021S1, Monash Business School", 
  2021, "Runner-up for AMSI Winter School Participants Talk, \\href{https://ws.amsi.org.au/}{Australian Mathematical Sciences Institute}",
  2021, "ACEMS Business Analytics Prize(\\$3000) for 2021, \\href{https://acems.org.au}{ARC Centre of Excellence for Mathematical \\& Statistical Frontiers}",
  2019, "Monash Graduate Scholarship, Monash University, yearly from 2019 to 2022",
  2019, "Monash International Tuition Scholarship, Monash University, yearly from 2019 to 2022",
  2018, "Outstanding Postgraduate Student, Central University of Finance and Economics (CUFE)",
  2017, "First Prize Academic Scholarship for Graduate Student, CUFE",
  2016, "Outstanding Undergraduate Student, CUFE",
  2016, "Scholarship for All-Round Development, CUFE, yearly from 2013 to 2016",
  2016, "Scholarship for Excellent Academic Innovation, CUFE",
  2015, "Excellent Prize in National Undergraduate Statistical Contest in Modeling, Statistical Education Society of China",
  2015, "\\small{Second Prize in Contemporary Undergraduate Mathematical Contest in Modeling}, \\newline
   China Society for Industrial and Applied Mathematics",
  2015, "National Endeavor Scholarship, Beijing Municipal Commission of Education",
  2014, "Scholarship for Excellent Student Cadre, CUFE",
  2013, "Excellent Student Cadre, School of Statistics and Mathematics, CUFE",
) %>%
  baretable()
```

# Referees

\href{https://robjhyndman.com/}{Professor Rob J Hyndman}

FAA FASSA

Department of Econometrics and Business Statistics

Monash University, VIC 3800, Australia

Email: rob.hyndman@monash.edu

Telephone: + 61 3 990 52358

\bigskip

\href{https://anastasiospanagiotelis.netlify.app/}{Associate Professor Anastasios Panagiotelis}

Director of the International Institute of Forecasters

Discipline of Business Analytics

University of Sydney, NSW 2006, Australia

Email: anastasios.panagiotelis@sydney.edu.au

Telephone: +61 2 9114 4742
